A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-18 main.Rmd
section 2.3 done

Current standards, provided by native `ts` object in R and extended by **zoo** [@zoo2005], and **xts** [@R-xts], organize temporal data in matrices with implicit time indexes. These objects were designed for modelling methods. The diagram correspondingly would place the model at the center of the analytical universe, and all the transformations, visualisations would hinge on that format. This is contrary to the tidyverse conceptualisation, which wholistically captures the full data workflow.

@@

This paper proposes a new tidy representation for temporal data and a unified framework to streamline the workflow from data pre-processing to visualization and forecasting, as an integral part of tidy data analysis.

>>>>

Current standards, provided by the native `ts` object in R, extended by **zoo** [@zoo2005], and **xts** [@R-xts], assemble temporal data into matrices with implicit time indexes. These objects were designed for modelling methods. The diagram in the style of Figure \ref{fig:tsibble-fit}, would place the model at the center of the analytical universe, and all the transformations, visualisations would hinge on that format. This is contrary to the tidyverse conceptualisation, which wholistically captures the full data workflow.

@@

This paper describes a new tidy representation for temporal data, and a unified framework to streamline the workflow from data pre-processing to visualization and forecasting, as an integral part of a tidy data analysis.
